Effects of sexual selection on non-sexual fitness components: a meta-analysis

### 2018-03-05 meta_analysis_sexual_selection_pop_fitness.Rmd
5/3 Getting close :)

---
title: 'Effects of sexual selection on non-sexual fitness components: a meta-analysis'
author: "Justin Cally, University of Melbourne"
subtitle: Supplementary Material
output:
  html_document:
    toc: true # table of content true
    toc_float: true # make 
    depth: 3  # upto three depths of headings (specified by #, ## and ###)
    number_sections: false  ## if you want number sections at each table header
    theme: yeti # lovely fonts and colours
    code_folding: hide # awesome buttons to show/hide the code
  pdf_document: default
---

```{r warning=FALSE, message=FALSE, results='hide'}
library(knitr)
library(pander)
library(compute.es)
library(metafor)
library(dplyr)
library(lme4)
library(forestplot)
library(ggplot2)
library(kableExtra)
library(MuMIn)
library(glmulti)
library(cowplot)
library(ggrepel)
library(reshape2)
library(RColorBrewer)
source("Vdodge_function.R") # nice function for ggplot
```

@@

####_ISI Web of Science_

@@

####_Scopus_

@@

### Additions to the literature search

@@

This latter criterion is likely to be contentious, because there is rarely enough data justify the assumption that a particular trait is (or is not) correlated with population fitness. We therefore relied on our best judgement when deciding which studies to exclude (see Table XXX). The inclusion/exlusion critera as applied to each study are detailed in **Table S1**.

@@

4. We also collected various covariates for some of the studies (**DATA TABLE**), which are discussed later.

## The effect size dataset

### Table of effect sizes

@@

kable(prelim.data, "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "500px")
```

@@

**SS Strength, Ratios and SS Density's (Column 7-9)**: Various ratios of the number of males to females and the total number of individuals kept together in an experiment

@@

**JIF**: Journal Impact factor at year of publication. Several impact factors were unable to be determined/found and are NA.

________________________________________________

@@

**Table S3:** Table of effect sizes included in our meta-analysis. See the text following the data table for an explanation of each column.
 <br/><br/> 
<input type=button class=hideshow></input>
```{r message=FALSE}
n.blind.ones <- (sum(prelim.data$Blind == "Blind"))
prelim.data %>% 
  summarise(
    Effect_sizes_.Totalq = n(), 
    Publications = prelim.data$Study.ID %>% unique() %>% length(),
    Blind_experiments = n.blind.ones,
    Effect_sizes_.Stressedq = (sum(prelim.data$Environment == "Stressed")),
    Effect_sizes_.Unstressedq = (sum(prelim.data$Environment == "Unstressed")),         
    Effect_sizes_.Maleq = (sum(prelim.data$Sex == "M")),
    Effect_sizes_.Femaleq = (sum(prelim.data$Sex == "F")),
    Effect_sizes_.Both_sexesq = (sum(prelim.data$Sex == "B")),
    Different_species =  prelim.data$Species %>% unique() %>% length(),
    Effect_sizes_.Beetleq = sum(Taxon == "Beetle"),
    Effect_sizes_.Flyq = sum(Taxon == "Fly"),
    Effect_sizes_.Mouseq = sum(Taxon == "Mouse"),
    Effect_sizes_.Nematodeq = sum(Taxon == "Nematode"),
    Effect_sizes_.Miteq = sum(Taxon == "Mite"),
    Effect_sizes_.Cricketq = sum(Taxon == "Cricket"),
    Effect_sizes_.Guppyq = sum(Taxon == "Guppy")) %>% melt() %>%
  mutate(variable = gsub("_", " ", variable),
         variable = gsub("[.]", "(", variable),
         variable = gsub("q", ")", variable)) %>% 
  rename_("n" = "value", " " = "variable") %>% 
  pander(split.cell = 40, split.table = Inf)
```
 <br/><br/> 
**Table S4:** Table of fitness outcomes included in our meta-analysis by sex.
 <br/><br/> 
<input type=button class=hideshow></input>
```{r}
Outcome_and_sex <- as.data.frame.matrix(table(prelim.data$Outcome, prelim.data$Sex))
colnames(Outcome_and_sex) <- cbind("Both", "Male", "Female")

@@

@@

#Generate a plot
p.meta <- prelim.data %>% 
  mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female")) %>%
  ggplot(aes(y=reorder(AuthorYear, -g), x = g, shape = Sex, color = Outcome.Class)) +
  geom_errorbarh(aes(xmin = lowerci, 
                     xmax = upperci), height = 0.1) +
  geom_point(size = 3) +  #Add data points and color them black
  scale_x_continuous(limits=c(-5, 5), name='Standardized Mean Difference (g)') +
  scale_color_discrete(name = "Relationship\nto fitness") + 
  ylab('Reference') + 
  geom_vline(xintercept=0, color='black', linetype='dashed')+
  facet_grid(Outcome_f~., scales= 'free', space='free')+
  theme(strip.text.y = element_text(angle = 0))
ggsave(plot = p.meta, filename = "figures/Big_forest_plot.eps", height = 25, width = 12)
p.meta
```
<br></br>
**Figure 1:** Forest plot of raw effect sizes and their 95% confidence intervals, grouped according to environment (stressed or unstressed) and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together). Rows with multiple data points denote studies that provided multiple effect sizes.

@@

### Effect size differs depending on the response variable

@@

### Exploring our data with the large set of covariates

@@

### Effect size differ slightly between taxa

First we want to run the model using a restricted dataset where we remove effect sizes with Ambiguous outcomes or environments that were not stated whether they were stressed or unstressed (confusing and confounding). In this model we use Sex, Environment, Taxon and the interaction between sex and environment as we hypothesise that the a stressful enviornment may be of greater importance to the female sex due to 'female demographic dominance', which essentially states that female fitness is more important to the overall population demographics and that most benefits or conversely costs will accrue to female fitness components.

```{r}
#Restrict the dataset for unambiguous outcomes and environments 
restricted.data <- prelim.data %>% 
  filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated") %>% 
  mutate(Sex = as.character(Sex), 
         Environment = as.character(Environment), 
         Outcome.Class.2 = as.character(Outcome.Class), 
         Enforced.Monogamy = as.character(Enforced.Monogamy))

@@

```{r, fig.height= 7.5, fig.width=10}
pd <- position_dodgev(height = .7)
Taxon.metaanlysis <- predictions.complete %>% ggplot(aes(x = pred, 
                                                         y= Environment, 
                                                         fill = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
  geom_errorbarh(aes(xmin = predictions.complete$ci.lb, 
                     xmax = predictions.complete$ci.ub,
                     color= Sex), 
                 height = 0, position = pd) +
  geom_point(position = pd, size=3, shape=21, color = "grey20") + 
  facet_grid(Taxon ~.)+
  ylab("Environment \n")+
  xlab("\nModel Prediction (Hedges g)")+
  xlim(-2, 2)+
  ggtitle('Effects of Sex and Stress on \nPopulation Fitness for Each Taxon')+
  scale_fill_brewer(palette = "Set1")+
  scale_color_brewer(palette = "Set1")

ggsave(plot = Taxon.metaanlysis, filename = "figures/Taxon_metaanalysis_plot.eps", height = 7.5, width = 10)
Taxon.metaanlysis
```

This model indicates quite a bit of heterogeneity between taxon. However, more striking is that confidence bands increase for taxa with low sample size. As previously shown, the beetle and fly taxa are the most heavily sampled and in the above figure have the narrowest confidence bands. The overall direction of effect does not change, although guppies and mice show effect sizes ~ 0. We can see from this that under stressed environments, females from all taxa appear to have greater fitness increase than males or 'both'.

@@

####Does sexual selection benefit populations in stressed environments more than unstressed environments? **AND** Do the benefits of sexual selection accrue more for female fitness components?

Here we run a three level model where the outcome is nested within a study (Study.ID). Other potential random effects include Species and Group.ID. However the estimate (variance from random effect) of these two other potential random effects tended towards zero and were dropped from the model. Additionally the model could be run with just Study.ID, but from our exploration of heterogeneity (below) we see that there is sufficient correlation (but not ICC = 1) between outcomes to include it as a random effect within the model.

@@

#And plot the results
pd <- position_dodgev(height = .5)
EnvSex.metaanalysis <- predictions.complete2 %>% ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
  geom_errorbarh(aes(xmin = predictions.complete2$ci.lb, 
                     xmax = predictions.complete2$ci.ub,
                     color = Sex), height = 0, position = pd) +
  geom_point(position = pd, size=3, shape=21, color = "grey20") + 
  ylab("Environment\n")+
  xlab("\nEffect Size (Hedges g)")+
  xlim(-.75, .75)+
  ggtitle('Effects of Sex and Stress \non Population Fitness')+
  scale_fill_brewer(palette = "Set1")+
  scale_color_brewer(palette = "Set1")

ggsave(plot = EnvSex.metaanalysis, filename = "figures/Environment_Sex_metaanalysis_plot.eps", height = 7.5, width = 10)
EnvSex.metaanalysis
```

@@

__________________________________
###Estimating Heterogeneity using _I^2^_ and exploring correlations

Let's obtain a _I^2^_ statistic using the formulas presented here: http://www.metafor-project.org/doku.php/tips:i2_multilevel_multivariate

There are different methods to obtain estimates of _I^2^_, they should be pretty similar though. Here we obtain an overall value of _I^2^_ that is weighted based on variance where estimates of heterogeneity are sourced from sigma^2^ of the respective models. 
```{r}
#There are two estimates of heterogeneity: A between cluster (between studies) and a within-cluster (outcomes within a study)

#This is for the model with outcome within study
W <- diag(1/restricted.data$var.g)
X <- model.matrix(model.complete2)
P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
100 * sum(model.complete2$sigma2) / (sum(model.complete2$sigma2) + (model.complete2$k-model.complete2$p)/sum(diag(P)))
```
This is a reasonably high _I^2^_ value but is relatively common in Ecology and Evolution (Nakagawa 2017).

@@

This indicates that 32.37 % of total heterogeneity is due to the **between study** heterogeneity and 68.275 % for **between outcome** heterogeneity between different outcomes. With the remaining 7.5 % due to sampling variance. Interestingly this might indicate that _I^2^_ would be largely reduced for a model restricted to a single outcome... Let's test this with our most common outcome...Reproductive Success

@@

## Meta-Analysis on Variance

@@

First, we setup our calculation by creating a a restricted dataset with only unabmiguous fitness outcomes and running the functions developed by Nakagawa et al. 2015:

@@

Secondly, we utilise those formulas to obtain lnCVR and var.CVR for all applicable effect sizes. Noting that not all of the dataset has means, SD and n; some were calculated from summary statistics and are not able to have lnCVR calculated:

@@

Although not previously done extensively, it seems that the best way to conduct this analysis is not through subsetting but through utilising model predictions as we did with Hedges' g previously. This can be done be utilising the same predict function but for lnCVR and var.lnCVR.

@@

```{r}
#Now try with multilevel model 
variance.model <- rma.mv(lnCVr, var.lnCVr, mods = ~ 1 + Sex + Environment + Sex:Environment, 
                         random = ~ 1 | Study.ID/Outcome, 
                         method = "REML", data = prelim.data2)
summary(variance.model)
```

@@

pd <- position_dodgev(height = .3)
var.plot <- predictions.variance %>% ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
  geom_errorbarh(aes(xmin = predictions.variance$ci.lb, 
                     xmax = predictions.variance$ci.ub,
                     color = Sex), 
                 height = 0, position = pd) +
  geom_point(position = pd, size=3, shape = 21, color= "grey20") + 
  ylab("Environment\n")+
  xlab("\nlnCVR")+
  xlim(-1.2, 1.2)+
  ggtitle('Meta-Analysis of Variance (Using Model Predictions)')+
  scale_fill_brewer(palette = "Set1")+
  scale_color_brewer(palette = "Set1")

ggsave(plot = var.plot, filename = "figures/Variance_plot.eps", height = 7.5, width = 10)
var.plot
```

From these predictions we see that environmental stress has a large impact on phenotypic variance, whereby phenotypic variance is lower for females than for males and under stressful conditions the phenotypic variance of females decreases. Indicating there is a narrowing of phenotypic variance under selection.

____________________
##Bias

###Funnel plots indicate potential but small amounts of publication bias

Checking for biases with a funnell plot. Note that the trim and fill method does not work with rma.mv objects. However we can perform Eggers test using the ``regtest()`` function. This tests for asymmetry via assessing relationships between effect size and a specified predictor. See ``?regtest`` for more information. Also the eggers test does not work for rma.mv objects. 
```{r}
#regtest(forest.model, predictor = "vi")

# I cut all these out, since the trim-and-fill doesn't work, and those sub-models probably don't make sense
# trim.ambig <- trimfill.rma.uni(model.Ambiguous)
# funnel.rma(trim.ambig)
# regtest(model.Ambiguous, predictor = "vi")
# funnel.rma(model.Indirect)
# regtest(model.Indirect, predictor = "vi")
# funnel.rma(model.Direct)
# regtest(model.Direct, predictor = "vi")
# funnel.rma(model.complete2, type="rstandard", yaxis = "sei")
```

>Now use ggplot for funnel plot. This is pretty clunky and unlike the ``funnel.rma`` it does not use residuals but raw effect sizes, we could of course add residuals, so it depends on how much customization you think these plots should have. The outline taken from: https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/

@@

@@

# Obtain grand mean effect size    <- ADDED BY LUKE
grand.mean <- as.numeric(forest.model$b)

@@

  ggplot(dataset, aes(x = sqrt(var.g), y = g)) +
    geom_point(size=1, shape = 21, color= "grey20") +
    xlab("Standard Error") + ylab("Effect size (Hedges' g)") +
    geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) + # confidence lines
    geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
    geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
    geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
    #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
    geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI, colour = "tomato") +
    geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI, colour = "tomato") +
    scale_x_reverse() +
    # scale_y_continuous(breaks = seq(-1.25,2,0.25)) + #Choose values that work for you based on your data
    coord_flip() +
    scale_fill_brewer(palette = "Set1")+
    theme_classic()
    # apatheme

@@

###Other tests of publication bias suggest there is little evidence for publication bias

####Journal Impact Factor

If we see a positive trend with effect size and Journal Impact Factor it may represent publication bias whereby significant (positive) results are published more readily and in more circulated journals. Our journal impact factor dataset is not evenly distributed as several publications in Nature (JIF ~ 40) are much larger than the next highest JIF (~11).

```{r, fig.height= 7.5, fig.width=10}
prelim.data %>% ggplot(aes(x=JIF, y=g))+
  geom_jitter(color='darkgreen', alpha=.3, aes(size = (1/(var.g))/sum((1/(var.g)))*100))+
  geom_hline(yintercept=0, linetype = 'dotted')+
  geom_smooth(method='lm', color='black')+
  labs(size = 'Weight (%)', y='Effect size (Hedges g)', x= 'Journal Impact Factor')
```

> Is this graph ok how it is?

#### Time-lag Bias

We can also look at the time-lag bias, which suggests effect size decreases over time. Again, because one publication from 1980 is well before the next publication in the late 1990s we see a very uneven distribution.

```{r, fig.height= 7.5, fig.width=10}
prelim.data %>% 
  ggplot(aes(x=Year, y=g))+
  geom_jitter(color='darkorange', alpha=.5, aes(size = (1/(var.g))/sum((1/(var.g)))*100))+
  geom_hline(yintercept=0, linetype = 'dotted')+
  geom_smooth(method='lm', color='black')+
  labs(size = 'Weight (%)', y='Effect size (Hedges g)', x= 'Year')
```

#### Blinding

From these graphs, we see a small trend for larger effect sizes to be published in higher impact journals as well as for effect size to decrease over successive years. Additionally to publication bias, other forms of bias may exist within studies. We initially collected data on whether studies were blind or not. Although not enough studies (n=8) used blinding for us to include it as a fixed effect within the model we can test whether blinding affects the raw effect size:

>>>>

---
title: 'Effects of sexual selection on non-sexual fitness components: a meta-analysis'
author: "Justin G. Cally^1^, Luke Holman^1^, Devi Stuart-Fox^1^ <br></br> <br></br> ^1^The University of Melbourne"
subtitle: Supplementary Material
output:
  html_document:
    toc: true # table of content true
    toc_float: true # make 
    depth: 3  # upto three depths of headings (specified by #, ## and ###)
    number_sections: false  ## if you want number sections at each table header
    theme: yeti # lovely fonts and colours
    code_folding: hide # awesome buttons to show/hide the code
  pdf_document: default
---

```{r warning=FALSE, message=FALSE, results='hide'}
library(knitr)
library(pander)
library(compute.es)
library(metafor)
library(dplyr)
library(lme4)
library(forestplot)
library(ggplot2)
library(kableExtra)
library(ggrepel)
library(reshape2)
library(RColorBrewer)
source("Vdodge_function.R") # nice function for ggplot
```

@@

<br></br>

**_ISI Web of Science_**

@@

<br></br>

**_Scopus_**

@@

### Additions to the Literature Search

@@

This latter criterion is likely to be contentious, because there is rarely enough data justify the assumption that a particular trait is (or is not) correlated with population fitness. We therefore relied on our best judgement when deciding which studies to exclude (see Table **XXX**). The inclusion/exlusion critera as applied to each study are detailed in **Table S1**.

@@

4. We also collected various covariates for some of the studies (**Table S2**), which are discussed later.

______________

## The Effect Size Dataset

### Table of Effect Sizes

>Justin Says: I think I need to clean up some of the notes and make them more readable

@@

kable(prelim.data, "html") %>%
  kable_styling() %>%
  scroll_box(width = "800px", height = "500px")
```
<br></br>

@@

**SS Strength, Ratios and SS Density's (Column 7-9)**: Various ratios of the number of males to females and the total number of individuals kept together in an experiment [Was not used in any analysis]

@@

**JIF**: Journal Impact factor at year of publication. Several impact factors were unable to be determined/found and are NA.
<br></br>

@@

**Table S3:** Table of effect sizes included in our meta-analysis. See the text following the data table for an explanation of each column.
 <br/><br/> 
<input type=button class=hideshow></input>
```{r message=FALSE, warning=FALSE}
n.blind.ones <- (sum(prelim.data$Blind == "Blind"))
prelim.data %>% 
  summarise(
    Effect_sizes_.Totalq = n(), 
    Publications = prelim.data$Study.ID %>% unique() %>% length(),
    Blind_experiments = n.blind.ones,
    Effect_sizes_.Stressedq = (sum(prelim.data$Environment == "Stressed")),
    Effect_sizes_.Unstressedq = (sum(prelim.data$Environment == "Unstressed")),         
    Effect_sizes_.Maleq = (sum(prelim.data$Sex == "M")),
    Effect_sizes_.Femaleq = (sum(prelim.data$Sex == "F")),
    Effect_sizes_.Both_sexesq = (sum(prelim.data$Sex == "B")),
    Different_species =  prelim.data$Species %>% unique() %>% length(),
    Effect_sizes_.Beetleq = sum(Taxon == "Beetle"),
    Effect_sizes_.Flyq = sum(Taxon == "Fly"),
    Effect_sizes_.Mouseq = sum(Taxon == "Mouse"),
    Effect_sizes_.Nematodeq = sum(Taxon == "Nematode"),
    Effect_sizes_.Miteq = sum(Taxon == "Mite"),
    Effect_sizes_.Cricketq = sum(Taxon == "Cricket"),
    Effect_sizes_.Guppyq = sum(Taxon == "Guppy")) %>% melt() %>%
  mutate(variable = gsub("_", " ", variable),
         variable = gsub("[.]", "(", variable),
         variable = gsub("q", ")", variable)) %>% 
  rename_("n" = "value", " " = "variable") %>% 
  pander(split.cell = 40, split.table = Inf)
```
 <br/><br/> 
**Table S4:** Table of fitness outcomes included in our meta-analysis by sex.
 <br/><br/> 
<input type=button class=hideshow></input>
```{r}
Outcome_and_sex <- as.data.frame.matrix(table(prelim.data$Outcome, prelim.data$Sex))
colnames(Outcome_and_sex) <- cbind("Both", "Male", "Female")

@@

```
<br></br>

@@

#Generate a plot
p.meta <- prelim.data %>% 
  mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female")) %>%
  ggplot(aes(y=reorder(AuthorYear, -g), x = g, shape = Sex, color = Outcome.Class)) +
  geom_errorbarh(aes(xmin = lowerci, 
                     xmax = upperci), height = 0.1) +
  geom_point(size = 1.5) +
  scale_x_continuous(limits=c(-5, 5), name='Standardized Mean Difference (g)') +
  scale_color_discrete(name = "Relationship\nto fitness") + 
  ylab('Reference') + 
  geom_vline(xintercept=0, color='black', linetype='dashed')+
  facet_grid(Outcome_f~., scales= 'free', space='free')+
  theme(strip.text.y = element_text(angle = 0))
ggsave(plot = p.meta, filename = "figures/Big_forest_plot.eps", height = 25, width = 12)
p.meta
```
<br></br>
**Figure S1:** Forest plot of raw effect sizes and their 95% confidence intervals, grouped according to environment (stressed or unstressed) and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together). Rows with multiple data points denote studies that provided multiple effect sizes.

@@

## Multilevel Meta-Analysis

@@

### Models With Many Covariates

@@

### Sexual Selection Amongst Taxa

First we want to run the model using a restricted dataset where we remove effect sizes with Ambiguous outcomes (directionless or variable in their relation to fitness) or environments that were not stated whether they were stressed or unstressed (confusing and confounding). In this model we use Sex, Environment, Taxon and the interaction between sex and environment as we hypothesise that the a stressful enviornment may be of greater importance to the female sex due to 'female demographic dominance', which essentially states that female fitness is more important to the overall population demographics and that most benefits or conversely costs will accrue to female fitness components.

```{r, warning=FALSE}
#Restrict the dataset for unambiguous outcomes and environments 
restricted.data <- prelim.data %>% 
  filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated") %>% 
  mutate(Sex = as.character(Sex), 
         Environment = as.character(Environment), 
         Outcome.Class.2 = as.character(Outcome.Class), 
         Enforced.Monogamy = as.character(Enforced.Monogamy))

@@

```{r, fig.height= 7.5, fig.width=10}
pd <- position_dodgev(height = .7)
Taxon.metaanlysis <- predictions.complete %>% 
    mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female")) %>%
  ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
  geom_errorbarh(aes(xmin = predictions.complete$ci.lb, 
                     xmax = predictions.complete$ci.ub,
                     color= Sex), 
                 height = 0, position = pd, show.legend = F) +
  geom_point(position = pd, size=3, shape=21, color = "grey20") + 
  facet_grid(Taxon ~.)+
  ylab("Environment \n")+
  xlab("\nModel Prediction (Hedges g)")+
  xlim(-2, 2)+
  ggtitle('Effects of Sex and Stress on \nPopulation Fitness for Each Taxon')+
  scale_fill_brewer(palette = "Set1")+
  scale_color_brewer(palette = "Set1")+
  guides(fill = guide_legend(reverse=T))

ggsave(plot = Taxon.metaanlysis, filename = "figures/Taxon_metaanalysis_plot.eps", height = 7.5, width = 10)
Taxon.metaanlysis
```
<br></br>
**Figure S2:** The predictions from this model indicate some heterogeneity between taxon. However, the most apparent difference between taxa is that confidence bands increase for taxa with low sample size. As previously shown, the beetle and fly taxa are the most heavily sampled and in the above figure have the narrowest confidence bands. Importantly, the overall direction of effect does not change between taxon, although guppies and mice show near zero effect sizes. Here we see that under stressed environments, females from all taxa appear to have greater fitness increase than males or 'both'.

@@

###Sexual Selection, Environment and Sex

Here we ask two key questions: Does sexual selection benefit populations in stressed environments more than unstressed environments? **AND** Do the benefits of sexual selection accrue more for female fitness components?

We run a three level model where the outcome is nested within a study (Study.ID). Other potential random effects include Species and Group.ID. However the estimate (variance from random effect) of these two other potential random effects tended towards zero and were dropped from the model. Additionally the model could be run with just Study.ID, but from our exploration of heterogeneity (below) we see that there is sufficient correlation (but not ICC = 1) between outcomes to include it as a random effect within the model.

@@

#And plot the results
pd <- position_dodgev(height = .5)
EnvSex.metaanalysis <- predictions.complete2 %>% 
      mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female")) %>%
  ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
  geom_errorbarh(aes(xmin = predictions.complete2$ci.lb, 
                     xmax = predictions.complete2$ci.ub,
                     color = Sex), height = 0, position = pd, show.legend = F) +
  geom_point(position = pd, size=3, shape=21, color = "grey20") + 
  ylab("Environment\n")+
  xlab("\nEffect Size (Hedges g)")+
  xlim(-.75, .75)+
  ggtitle('Effects of Sex and Stress \non Population Fitness')+
  scale_fill_brewer(palette = "Set1")+
  scale_color_brewer(palette = "Set1")+
  guides(fill = guide_legend(reverse=T))

ggsave(plot = EnvSex.metaanalysis, filename = "figures/Environment_Sex_metaanalysis_plot.eps", height = 7.5, width = 10)
EnvSex.metaanalysis
```
<br></br>
**Figure S3:** Sexual selection generally increases population fitness, especially for females under stressed conditions. The benefits of sexual selection on fitness for females under stressed conditions are small-medium according to Cohen's interperetation of effect sizes.

@@

__________________________________
###Estimating Heterogeneity Using _I^2^_

Let's obtain a _I^2^_ statistic for the model above using the formulas presented here: http://www.metafor-project.org/doku.php/tips:i2_multilevel_multivariate

There are different methods to obtain estimates of _I^2^_, they should be pretty similar though. Here we obtain an overall value of _I^2^_ that is weighted based on variance where estimates of heterogeneity are sourced from sigma^2^ of the respective models. 
```{r}
#This is for the model with outcome and study as crossed random effects
W <- diag(1/restricted.data$var.g)
X <- model.matrix(model.complete2)
P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
100 * sum(model.complete2$sigma2) / (sum(model.complete2$sigma2) + (model.complete2$k-model.complete2$p)/sum(diag(P)))
```
This is a reasonably high _I^2^_ value but is relatively common in Ecology and Evolution (Nakagawa 2017).

@@

This indicates that 32.37 % of total heterogeneity is due to the **between study** heterogeneity and 62.17 % for **between outcome** heterogeneity between different outcomes. With the remaining 5.5 % due to sampling variance. Interestingly this might indicate that _I^2^_ would be largely reduced for a model restricted to a single outcome... Let's test this with our most common outcome...Reproductive Success

@@

## Multilevel Meta-Analysis on Variance

@@

**Firstly**, we setup our calculation by creating a a restricted dataset with only unabmiguous fitness outcomes and running the functions developed by Nakagawa et al. 2015:

@@

**Secondly**, we utilise those formulas to obtain lnCVR and var.CVR for all applicable effect sizes. Noting that not all of the dataset has means, SD and n; some were calculated from summary statistics and are not able to have lnCVR calculated:

@@

**Thirdly**, although not previously done extensively, it seems that the best way to conduct this analysis is not through subsetting but through utilising model predictions as we did with Hedges' g previously, that way we retain the same methodology in model structure and test the same hypotheses. This can be done be utilising the same predict function but for lnCVR and var.lnCVR.

@@

```{r, warning=FALSE}
#Now try with multilevel model 
variance.model <- rma.mv(lnCVr, var.lnCVr, mods = ~ 1 + Sex*Environment, 
                          random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome), 
                         method = "REML", data = prelim.data2)
summary(variance.model)
```

@@

pd <- position_dodgev(height = .3)
var.plot <- predictions.variance %>% 
 mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
        Sex = replace(Sex, Sex == "M", "Male"),
        Sex = replace(Sex, Sex == "F", "Female")) %>%
  ggplot(aes(x = pred, y= Environment, fill = Sex)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
  geom_errorbarh(aes(xmin = predictions.variance$ci.lb, 
                     xmax = predictions.variance$ci.ub,
                     color = Sex), 
                 height = 0, position = pd, show.legend = F) +
  geom_point(position = pd, size=3, shape = 21, color= "grey20") + 
  ylab("Environment\n")+
  xlab("\nlnCVR")+
  xlim(-1.2, 1.2)+
  ggtitle('Meta-Analysis of Variance (Using Model Predictions)')+
  scale_fill_brewer(palette = "Set1")+
  scale_color_brewer(palette = "Set1")+
  guides(fill = guide_legend(reverse=T))

ggsave(plot = var.plot, filename = "figures/Variance_plot.eps", height = 7.5, width = 10)
var.plot
```
<br></br>
**Figure S4:** Phenotypic variation changes under sexual selection in stressful environments. For stressed females, phenotypic variation decreases (narrows). While for males in stressed environments it increases. For outcomes that measured both males and females (both) phenotypic variation did not change **or** changed for males and females in opposite directions and thus cancels out when measured together.

____________________
##Publication Bias

###Funnel plots and Egger's Test

Checking for biases with a funnel plot. Note that the trim and fill method does not work with rma.mv objects. However we can perform Eggers test using the ``regtest()`` function. This tests for asymmetry via assessing relationships between effect size and a specified predictor. See ``?regtest`` for more information. Because the Eggers test does not work for ``rma.mv`` objects we remove the random effects and run with Sex * Environment as moderators. 
```{r}
standard.model <- rma(g, var.g, 
                      mods = ~ 1 + Sex * Environment, 
                      data=prelim.data)
regtest(standard.model)
```

We can use ggplot for creating a funnel plot. The code is pretty clunky and unlike the ``funnel.rma`` it does not use automatically plot residuals so we have to generate them independently. The outline taken from: https://sakaluk.wordpress.com/2016/02/16/7-make-it-pretty-plots-for-meta-analysis/

@@

```{r, fig.height= 7.5, fig.width=10, warning=FALSE, message=FALSE}

@@

# Obtain grand mean effect size    <- ADDED BY LUKE
grand.mean <- as.numeric(forest.model$b) #WHAT about weightings?

@@

  ggplot(dataset, aes(x = sqrt(var.g), y = g)) +
    geom_point(size=1, shape = 21, color= "grey20") +
    xlab("Standard Error") + ylab("Effect size (Hedges' g)") +
    geom_line(aes(x = se.seq, y = ll95), linetype = 'dotted', data = dfCI) + # confidence lines
    geom_line(aes(x = se.seq, y = ul95), linetype = 'dotted', data = dfCI) +
    geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
    geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
    #Now plot dotted lines corresponding to the 95% CI of your meta-analytic estimate
    geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='dotted', data=dfCI, colour = "tomato") +
    geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='dotted', data=dfCI, colour = "tomato") +
    scale_x_reverse() +
    # scale_y_continuous(breaks = seq(-1.25,2,0.25)) + #Choose values that work for you based on your data
    coord_flip() +
    scale_fill_brewer(palette = "Set1")
    # theme_classic()
    # apatheme

@@

```
<br></br>
**Figure S5:** A funnel plot of 459 effect sizes shows asymmetry, indicating potential publication bias, egger's regression test for funnel plot asymmetry also suggests the plot is asymmetrical (z = 7.2671, p < .0001). The asymmetry appears to be sourced from a spread of positive effect sizes outside the funnel and of varying degrees of precision. Counter to expectations of publication bias these positive studies are not just 'low precision, large effect' results. Funnel plot asymmetry may also be due to heterogeneity, which in this study is high due to the many species and outcomes measured.

###Journal Impact Factor

If we see a positive trend with effect size and Journal Impact Factor (JIF) it may represent publication bias whereby significant (positive) results are published more readily and in more circulated journals and non-confirmitory or negative results are not published or publiushed in lower impact journals. Our journal impact factor dataset is not evenly distributed as several publications in Nature (JIF ~ 40) are much larger than the next highest JIF (~11).

```{r, fig.height= 7.5, fig.width=10, warning=FALSE}
JIF.plot <- prelim.data %>% ggplot(aes(x=JIF, y=g))+
  geom_jitter(color='darkgreen', alpha=.3, aes(size = (1/(var.g))/sum((1/(var.g)))*100))+
  geom_hline(yintercept=0, linetype = 'dotted')+
  geom_smooth(method='lm', color='black')+
  scale_x_continuous(breaks = c(0,10,20,30,40), limits = c(2,42.5))+
  labs(size = 'Weight (%)', y='Effect size (Hedges g)', x= 'Journal Impact Factor')

ggsave(plot = JIF.plot, filename = "figures/JIF_plot.eps", height = 7.5, width = 10)
JIF.plot
```
<br></br>
**Figure S6:** Journal impact factor does not show a noticable correlation with effect size. The positive slope shown here is due to several effect sizes published in a high impact journal. Most papers were published in discipline specific journals such as _Evolution_ and _Journal of Evolutionary Biology_.

### Time-lag Bias

We can also look at the time-lag bias, which suggests effect size decreases over time. Again, because one publication from 1980 is well before the next publication in the late 1990s we see a very uneven distribution of data points.

```{r, fig.height= 7.5, fig.width=10, warning=FALSE}
time.plot <- prelim.data %>% 
  ggplot(aes(x=Year, y=g))+
  geom_jitter(color='darkorange', alpha=.5, aes(size = (1/(var.g))/sum((1/(var.g)))*100))+
  geom_hline(yintercept=0, linetype = 'dotted')+
  geom_smooth(method='lm', color='black')+
  labs(size = 'Weight (%)', y='Effect size (Hedges g)', x= 'Year')
